---
title: "Project 2"
author: "Madeleine Ashby"
date: "10/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Import necessary libraries / packages
library(readxl)
library(dplyr)
library(ggplot2)
library(tstools)
library(zoo)
library(ggwordcloud)
library(tidytext)
library(textdata)
```

# Hypothesis

Using sentiment analysis performed on climate change tweets globally, at least 75% of the tweets will be classified as negative sentiment.


# Exploratory Data Analysis

## Data Collection

In order to explore our hypothesis, we needed to find Twitter datasets about climate change. The data we are using was obtained from Kaggle and can be found at this [link](https://www.kaggle.com/datasets/die9origephit/climate-change-tweets).  The data lists the top Tweets about climate change and initially consists of 11 columns.

## Data Cleaning
```{r}
# Load in data
climate_change <- read_excel("C:/Users/Maddie/Documents/DS 4002/Project 2/ClimateChange.xlsx")

# Clean up whack characters
climate_change$Embedded_text <- gsub("’", "'", climate_change$Embedded_text)
climate_change$Embedded_text <- gsub("“", " ", climate_change$Embedded_text)


# Drop unnecessary columns
climate_change <- climate_change[-c(1,2,4,6,7,10,11)]

# Rename columns
climate_change <- climate_change %>%
  rename(
    `Embedded Text` = Embedded_text
  )
```

```{r}
# Popularity Rating based on Likes
climate_change <- climate_change %>%
  mutate(Popularity = ifelse(Likes <=1890, 1,
                             ifelse(Likes <= 3780, 2,
                                    ifelse(Likes <= 5670, 3,
                                           ifelse(Likes <= 7560, 4, 5)))))
```


```{r}
# Number of Tweets about Climate Change from 1/1/2022 to 7/17/2022
nrow(climate_change)
```

```{r}
# Barplot of number of tweets per popularity group
ggplot(climate_change, aes(x=Popularity)) + geom_bar() + theme_minimal() + ggtitle("Number of Tweets per Popularity Level")
```

```{r}
# Number of tweets per month
climate_change$Timestamp <- format(as.Date(climate_change$Timestamp), "%Y-%m")
ggplot(climate_change, aes(x=Timestamp)) + geom_histogram(bins=7, stat="count") +
  ggtitle("Number of Tweets per Month") + xlab("Month") + ylab("Count")

```

# Analysis

```{r}
#Prepare data for sentiment analysis

# Make all text in one string
all_climate_text <- toString(climate_change$`Embedded Text`)
all_climate_text <- as.data.frame(all_climate_text)
all_climate_text <- all_climate_text %>%
  rename(
    text = all_climate_text
  )

# Tokenize (make each word its own column)
all_climate_text <- all_climate_text %>%
  unnest_tokens(word, text)

# Remove stop words
all_climate_text <- all_climate_text %>%
  anti_join(stop_words)

# Remove duplicates
no_duplicates <- all_climate_text$word[!duplicated(all_climate_text$word)]
no_duplicates <- as.data.frame(no_duplicates)

# Rename column 
no_duplicates <- no_duplicates %>% 
  rename(
    word = no_duplicates
  )
```

## AFINN Sentiment Analysis
```{r}
# Create a table ith words and sentiment rating
climate_change_afinn <- no_duplicates %>%
  inner_join(get_sentiments("afinn"))

# Understand
summary(climate_change_afinn)

# Visualize
ggplot(data = climate_change_afinn,
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("Climate Change AFINN Sentiment Range")+
  theme_light()

# To test hypothesis: 64.01% negative
temp_count <- 0

for (x in 1:nrow(climate_change_afinn)){
  if (climate_change_afinn$value[x] < 0){
    temp_count <- temp_count + 1
  }
}

print(temp_count/nrow(climate_change_afinn))

```

## NRC Sentiment Analysis
```{r}
# Create table with words and sentiment description
climate_change_nrc <- no_duplicates %>%
  inner_join(get_sentiments("nrc"))

# Visualize
table(climate_change_nrc$sentiment)
ggplot(climate_change_nrc, aes(x=sentiment)) + geom_bar() + theme_minimal() + ggtitle("Frequency per NRC Sentiment Category")

# To test hypothesis: 56.97% negative
# Negative sentiment: anger, disgust, fear, negative, sadness, anticipation
print((613 + 470 + 748 + 1516 + 610) / nrow(climate_change_nrc))

```

## Bing Sentiment Analysis
```{r}
# Create a table with words and sentiment description
climate_change_bing <- no_duplicates %>%
  inner_join(get_sentiments("bing"))

# Visualize
table(climate_change_bing$sentiment)
ggplot(climate_change_bing, aes(x=sentiment)) + geom_bar() + theme_minimal() + ggtitle("Frequency per Bing Sentiment Category")

# To test hypothesis:67.43% negative sentiment
print(1706/(1706+824))

```

## TF Analysis
```{r}
# Calculate word count for each word
word_count <- all_climate_text %>%
  count(word, sort = TRUE)

# Calculate total number of words
total_words <- word_count %>%
  summarize(total = sum(n))

# Join values together
climate_words <- left_join(word_count, total_words, by = character())

# Temporary variables for computing term frequency
freq <- 1:35134
tf <- data.frame(word_count$word, freq)

for (x in 1:nrow(climate_words)) {
  tf$freq[x] <- word_count$n[x] / 263492
}

# Add term frequency to climate_words data frame
climate_words <- mutate(climate_words, term_frequency = tf$freq)
```



